% ============================================================
% Example: English Love Letter using vintageletter class
% Compile with: xelatex example-english.tex
% ============================================================
\documentclass{../vintageletter}

\begin{document}

% ── Addressee ──────────────────────────────────────────────
\addressee{To My Dearest Beloved,}

% ── Body ────────────────────────────────────────────────────
It has been some time since I last wrote to you, and for that, I must beg your forgiveness. Yet know this: my affection for you has only deepened with each passing day, growing like a garden tended by patient hands. The words I now set upon this page have long dwelt in my heart, too precious to speak aloud, too fragile to risk upon the winds of casual conversation.

\ornrule

In the quiet hours before dawn, I find myself thinking of you. The morning light reminds me of your smile; the evening stars, of the brightness of your eyes. You have become the measure by which I judge all beauty, the standard against which all else falls short.

They say that love is a madness, and perhaps they are right. For I find myself quite unable to concentrate upon my daily tasks, my mind wandering constantly to thoughts of you. A letter from you would sustain me for days; your silence leaves me wandering like a soul unmoored.

\ornrule

I beg you, do not turn away from these words. Grant me but a single line in reply, and I shall treasure it as a miser treasures gold. Tell me that I have not presumed too much in declaring what my heart has known for so long.

You hold my heart in your hands, though you may not know it. Every beat of it speaks your name. Every dream I have features your face. You are the first thought upon waking, the last before sleep claims me.

\ornrule

Some may say that friendship is the only bond permitted between us, given our circumstances. But I tell you truly: what I feel transcends such boundaries. This devotion will not fade with time, nor will this burning passion cool. I am yours, in whatever capacity you will have me—friend, companion, or something more that words have not yet named.

\ornrule

Until I hear from you, I remain,

\begin{dedication}
Yours eternally,
\end{dedication}

\signature{A.}

\end{document}
